\LARGE \bf ``Those who can't do, teach'': a Teachable Robotic Agent for Children Learning Handwriting

### 2014-09-16 main.tex
Re-organize the last part of the paper
{Conclusion} -> {Towards long-term intervention + Conclusion}

\begin{figure}[thpb]
     \begin{center}
        %\subfigure{
        %    \includegraphics[width=0.4\textwidth]{figures/naoWriting1.png}
        %}%
        \subfigure{
            \includegraphics[width=0.3\textwidth]{figures/naoWriting2.png}
        }%
%
    \end{center}
    \caption{A demonstration of the robot simulating the writing of a word with
    its finger. The motion of the robot is synchronised with the display of the
    tablet, communicating over ROS.}%

@@

\begin{figure}[htpb]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/chilitagDetection_cameraOverlay.png}
    \caption[Detection of the tablet using a chilitag to represent the origin of
    the writing surface frame.]{\label{fig:tabletDetection}Detection of the
    tablet using a chilitag to represent the origin of the writing surface frame
(left: robot's camera image, with markers overlaid).}

@@

\subsection{Integration into a Robotic Handwriting Learning Agent}

@@

\subsection{Discussion}% * <deanna.m.hood@gmail.com> 2014-09-05T11:42:42.979Z:
%
% this is a reasonable title right?
%

In addition to the conclusions which 
Anecdotes which raise questions:
- "Would have problems with the 'n'" - (8) projecting human learning characteristics. Another said "programmed to write badly" (4)
- Children saying the other was bad... (3, 9). Child saying the other child's was good (5). Child saying the robot was better than him (9).
- When one child wrote u differently to the other, they didn't discuss :(
- so many of them wanted to write the whole word.. robot says "show me a word" and maybe misleading
- not seeming to notice small changes (12) but maybe from experimenter

- awkward silence, speaking over the top of the robot to talk to experimenter....
- child walking around
- word very close to robot's camera

Evidence of engagement:
- work and/or play
- once word was good were thinking for a long time about how to improve (8)
- child `helping' other.. grabbing the pen
- children trying to cheat the system (10)
- excitement at stop and test cards - new letters? diff font
- teaching cursive. group 7 excited to do this even after test finished.
- unnecessary (unsent) demo from child 11 after it was acceptable but not perfect

\paragraph{Role of the experimenter}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}

%\subsection{Conclusions}

The technical challenges involved in developing a teachable robotic agent in the
context of handwriting which have been addressed in this work include:

@@

\subsection{Future Work}

Further research may discover how to best model/limit the learning speed of the
robot so that it is noticeably learning while not improving so fast as to limit
the long-term interaction potential for the system, which may turn out to be
child-dependent.

In terms of the interaction experience, the current experimental setting, while
technically autonomous, can not robustly recover from situations outside of the
nominal protocol (presented in Section~\ref{sec4}), and consequently still requires the
presence of an experimenter. The interaction state machine would require to be
extended in non-trivial ways to allow for long, fully autonomous, interactions
with children.

On the educational side, open questions include how the handwriting error
generation of the system may be abstracted to a higher level of control so that
a teacher may configure it to work with a child on a particular type of
mistakes, based on the child's performance. Where would the balance lie between
developing autonomous capabilities for the system to determine the child's
difficulties, and empowering the teaching staff to decide for themselves
instead? And, as a result, the ultimate question for this area of research is
to address what impact to the outcomes of a long-term handwriting intervention the
addition of such a teachable robotic agent would have: does it impact the
motivation of the participants, their self-esteem, and/or the learning gains
that they experience? We are currently considering running a long-term study
(about 20 hours of interactions per child) that would provide better evidences
to answer these questions.

\subsection{Impact and Conclusion}

Because it has the strongest impact for the human-robot interaction community,
we would like to develop this last point in particular. The work presented here
investigates a particular role for a robot in the education of handwriting: not
only the robot is actively performing the activity (it draws letters), but it
does so in a way that engages the child in a very specific social role. The child
is the teacher, the robot is the learner: the child must engage in a
(meta-)cognitive relation with the robot to try to understand why the
robot fails and how to help it best.  Here, the robot is not only an activity
facilitator or orchestrator: its physical presence and embodiment induce agency
and anthropomorphizing, and cognitively engage the child into the learning
activity, which we predict to lead to higher learning efficacy.

>>>>

\begin{figure}[thpb]
     \begin{center}
        %\subfigure{
        %    \includegraphics[width=0.4\textwidth]{figures/naoWriting1.png}
        %}%
        \subfigure{
            \includegraphics[width=0.9\linewidth]{figures/naoWriting2.png}
        }%
%
    \end{center}
    \caption{A demonstration of the robot simulating the writing of a word with
    its finger. The motion of the robot is synchronised with the display of the
    tablet, communicating over ROS.}%

@@

\begin{figure}[htpb]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/chilitagDetection_cameraOverlay.png}
    \caption{\label{fig:tabletDetection}Detection of the tablet using a fiducial
    marker to represent the origin of the writing surface frame. The robot's
    camera image is on the left (the text trajectory overlay is also visible).}

@@

\subsection{Integration into a Robotic Agent}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Towards Long-term Interventions}

As noted in the introduction, existing literature on handwriting interventions
agrees to consider 20 hours spread over 20 weeks as a reasonable intervention
duration to measure actual effects. This directly questions how suitable is our
approach for such long-term interactions, and raises several challenges, both
technical and human.

In terms of the interaction experience, the current experimental setting, while
technically autonomous, can not robustly recover from situations outside of the
nominal protocol (presented in Section~\ref{sec4}), and consequently still
requires the presence of an experimenter. The interaction state machine would
require to be extended in non-trivial ways to allow for long, fully autonomous,
interactions with children. Also, further research may discover how to best
model/limit the learning speed of the robot so that it is noticeably learning
while not improving so fast as to limit the long-term interaction potential for
the system, which may turn out to be child-dependent.

On the educational side, open questions include how the handwriting error
generation of the system may be abstracted to a higher level of control so that
a teacher may configure it to work with a child on a particular type of
mistakes, based on the child's performance. Where would the balance lie between
developing autonomous capabilities for the system to determine the child's
difficulties, and empowering the teaching staff to decide for themselves
instead? And, as a result, the ultimate question for this area of research is
to address what impact to the outcomes of a long-term handwriting intervention the
addition of such a teachable robotic agent would have: does it impact the
motivation of the participants, their self-esteem, and/or the learning gains
that they experience? We are currently considering running a long-term study
that would provide better evidences to answer these questions.

%In addition to the conclusions which 
%Anecdotes which raise questions:
%- "Would have problems with the 'n'" - (8) projecting human learning characteristics. Another said "programmed to write badly" (4)
%- Children saying the other was bad... (3, 9). Child saying the other child's was good (5). Child saying the robot was better than him (9).
%- When one child wrote u differently to the other, they didn't discuss :(
%- so many of them wanted to write the whole word.. robot says "show me a word" and maybe misleading
%- not seeming to notice small changes (12) but maybe from experimenter
%
%- awkward silence, speaking over the top of the robot to talk to experimenter....
%- child walking around
%- word very close to robot's camera
%
%Evidence of engagement:
%- work and/or play
%- once word was good were thinking for a long time about how to improve (8)
%- child `helping' other.. grabbing the pen
%- children trying to cheat the system (10)
%- excitement at stop and test cards - new letters? diff font
%- teaching cursive. group 7 excited to do this even after test finished.
%- unnecessary (unsent) demo from child 11 after it was acceptable but not perfect

\section{Impact and Conclusion}

Specifically, the technical challenges involved in developing a teachable
robotic agent in the context of handwriting which have been addressed in this
work include:

@@

However, we believe that the strongest impact of this work for the human-robot
interaction community relates to the very \emph{nature} of the interaction
fostered by this research. The work presented here investigates a particular
role for a robot in the education of handwriting: not only the robot is actively
performing the activity (it draws letters), but it does so in a way that engages
the child in a very specific social role. The child is the teacher, the robot is
the learner: the child must engage in a (meta-)cognitive relation with the robot
to try to understand why the robot fails and how to help it best.  Here, the
robot is not only an activity facilitator or orchestrator: its physical presence
and embodiment induce agency and anthropomorphizing, and cognitively engage the
child into the learning activity, which we predict to lead to higher learning
efficacy.
